Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
move running example section
review RUNNING EXAMPLE

@@

\blue{[Perhaps we should anticipate this example, partly showing potential repercussions of our formal approach. 
Indeed, this example does not show the full potential, since it does not start with the physical plant $G(s)$. ]}

A classical cruise control example is extracted from the
literature~\cite{Astrom08}, where the discrete plant model (with time step
of $0.2$s) is represented by the following z-expression:

\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimisation tool, 
the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed a high-performance controller that is characterised by the following z-domain transfer function:
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
However, if \red{[which ones? quantisation?] implementation aspects} are considered during verification, 
this controller becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16} \red{[clarify this notation]} 
implementation format can be represented by the following expression: 
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation} 
which makes the system unstable in closed-loop \red{using the typical series loop configuration [meaning?]}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Error Bound Verification}

%As described in the literature, computation using FWL leads to rounding and truncation errors~\cite{Oppenheim1999}. In the present work, impairments present on a closed-loop  system output, due to coefficient rounding and arithmetic-operation results, are considered. Let $x$ be a real number and $x^*$ be a floating-point representation of $x$. The absolute error $\epsilon$, due to the rounding of $x$ represented in floating-point as $x^*$, is 
%
%\begin{equation} \label{absolute-error}
%x^* = x + \epsilon,
%\end{equation}

%\noindent and the relative error $\delta$ by
%
%\begin{equation} \label{relative-error}
%x^* = x\left(1+\delta\right).
%\end{equation}

%The verification of output error bound is proposed, where the output of a closed-loop system, implemented with reduced-word-length floating-point representation, is compared with a reference output of the same structures, implemented using real variables.

%Thus, considering that the number of precision bits $l_{d}$ in reference models is higher than in designed models, the quantization error $E_{r}$ is given by
%\begin{equation} \label{errorfixlimits}
%-2^{-l-1} + 2^{-l_{d}-1} \leq E_{r} \leq 2^{-l-1} - 2^{-l_{d}-1}.
%\end{equation}

%The expression above shows that the error, computed with the proposed method, is affected by the precision of the reference model.

%For the reduced floating-point models, the computed values are saturated to the maximum representable number on overflow, or to the minimum on underflow; the same input is applied to both models. The input vector uses non-deterministic values from $\{ 2^{k-1}-2^{-l}, 2^{-l}, 0, -2^{-l}, 2^{k-1} \}$, that is, values for maximum and minimum amplitudes of the input signal. So, errors due to quantization and saturation are explored.

%During closed-loop operation unrolling, the cumulative error can increase beyond the quantization-error interval. The following literal is then generated, in order to check whether the output error is in accordance with an acceptable margin:
%\begin{equation} \label{errorcheck}
%	l_{no\_error} \Leftrightarrow \arrowvert y - y_{d} \arrowvert \leq M \cdot 2^{-l-1},
%\end{equation}

%\noindent where $y$ is the output of the designed system, $y_{d}$ is the output of the double precision system, and $M~2^{-l-1}$ is the tolerance margin. The verification process searches for the negation of this literal. When such a counterexample is found, it indicates that the output error is higher than expected for that controller realization.

>>>>

To exploit the present approach full potential, a dynamical plant that can present 
physical components must be considered. However, a discrete plant model can also demonstrate 
some benefits of the present approach, which considers FWL effects in the digital 
controller implementation. In particular, a classical cruise control example 
is extracted from the literature~\cite{Astrom08}, where the discrete plant model (with time step
of $0.2$s) is represented by the following z-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

Using an optimisation tool, the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed 
a high-performance controller, which is characterised by the following z-domain transfer function:
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
However, if implementation aspects are considered during verification ({\it e.g.}, fixed-point arithmetic 
and word-length), then this controller becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16} implementation format 
({\it i.e.}, $4$ bits for the integer part and $16$ bits for the fractional part)
can be represented by the following expression: 
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation} 
which makes the system unstable in closed-loop using fixed-point arithmetic and 
the typical series loop configuration, where $C_{q}\left(z\right)$ and $G\left(z\right)$ 
are in the forward path.

@@
